---
title: "ASNAP Political Data"
output: html_notebook
---


## Setup    
  Load the relevant libraries.
```{r message=TRUE, warning=TRUE}

rm(list = ls())
# .rs.restartR()


# data munging
library("tidyverse")
library("data.table")
# library("tidyquant")    # rolling calculations


# creating functions
library("rlang")

# munge dates
library("lubridate")


# viz
library("scales")
library("plotly")




library("tictoc")

# get tweets
# library("rtweet")

# NLP
# library("tidytext")
# library("syuzhet")
# library("googleLanguageR")

# graph analyses
# library("tidygraph")
# library("ggraph")

# # feature engineering and data prep
# library("recipes")
# library("caret")
# library("DMwR")
# 
# # to explore missing data
# library("visdat")
# library("naniar")
# 
# # modeling
# library("h2o")

```
  
    
  Session Info.
```{r}

sessionInfo()

```


  Setup the root directory.
```{r "setup", include = FALSE}

require("knitr")


# Use when running from AWS
# opts_knit$set(root.dir = "/home/rstudio/Dropbox/_AWS/twitter_dc_metro2/")


# Use when running from laptop
opts_knit$set(root.dir = "/Users/mdturse/Desktop/Analytics/snap_political_ads")

```
  
    
  Setting `wd` as the working directory.
```{r}

wd <- getwd()

wd

```


## Get the Data  
  
  Read in the .csv files.
```{r}

data_2018 <-
  read_csv(file = paste0(wd,
                         "/Data/Raw/",
                         "/PoliticalAds2018.csv"
                         )
           ) %>% 
  rename_all(funs(str_replace_all(., "\\W", "_")))

data_2019 <-
  read_csv(file = paste0(wd,
                         "/Data/Raw/",
                         "/PoliticalAds2019.csv"
                         )
           ) %>% 
  rename_all(funs(str_replace_all(., "\\W", "_")))


message("data_2018")
glimpse(data_2018)

message("data_2019")
glimpse(data_2019)

```
  
  Compare if the column names are the same
```{r}

ncol(data_2018)
ncol(data_2019)

setdiff(colnames(data_2018),
        colnames(data_2019)
        )

```
  
    
  Bind the rows to create a single dataset.
```{r}

data_20182019 <-
  bind_rows(data_2018 %>% mutate(data_yr = 2018),
            data_2019 %>% mutate(data_yr = 2019)
            ) %>% 
  mutate(StartDate = as_datetime(StartDate),
         EndDate = as_datetime(EndDate))
  

glimpse(data_20182019)
# View(data_20182019 %>% head(1000))


ids <-
  data_2018 %>% 
  head(10) %>% 
  pull(ADID)

# View(data_2018 %>% 
#        filter(ADID %in% ids) %>% 
#        select(ADID,
#               StartDate,
#               EndDate
#               ) %>% 
#        arrange(ADID)
#      )
# 
# View(data_20182019 %>% 
#        filter(ADID %in% ids) %>% 
#        select(ADID,
#               StartDate,
#               EndDate
#               ) %>% 
#        arrange(ADID)
#      )

rm(data_2018, data_2019)

```
  
    
  Make the data "tidy" - i.e., one row per `Interests` and one row per `Targeting_Geo___Postal_Code` (instead of having list-columns as in the original data).
```{r}

data_20182019_long <-
  data_20182019 %>% 
  mutate(interests_long = str_split(Interests,
                                    ",",
                                    ),
         language_long = str_split(Language,
                                   ",",
                                   ),
         advanced_demographics_long = str_split(AdvancedDemographics,
                                                ",",
                                                ),
         Targeting_Geo___Postal_Code_long = str_split(Targeting_Geo___Postal_Code,
                                                      ",",
                                                      )
         ) %>% 
  unnest(interests_long) %>% 
  unnest(language_long) %>% 
  unnest(advanced_demographics_long) %>% 
  unnest(Targeting_Geo___Postal_Code_long) %>% 
  arrange(ADID)


dim(data_20182019)
dim(data_20182019_long)


glimpse(data_20182019_long)
# View(data_20182019_long %>% head(1000))



# View(data_20182019 %>%
#        filter(ADID %in% ids) %>%
#        select(ADID,
#               Interests,
#               Targeting_Geo___Postal_Code
#               ) %>%
#        arrange(ADID)
#      )
# 
View(data_20182019_long %>%
       filter(ADID %in% ids) %>%
       select(ADID,
              Interests,
              interests_long,
              Targeting_Geo___Postal_Code,
              Targeting_Geo___Postal_Code_long
              ) %>%
       arrange(ADID)
     )


rm(data_20182019, ids)

```


## Variable Exploration
```{r}

dim(data_20182019_long)
summary(data_20182019_long)

```


## Minor Feature Engineering  
  
  Creating new features.
```{r}

add_features <-
  data_20182019_long %>% 
  mutate(cost_per_impression = Spend / Impressions,
         impressions_per_dollar = Impressions / Spend,
         ad_delivery_interval = interval(start = StartDate,
                                         end = EndDate
                                         ),
         ad_delivery_duration_sec = ad_delivery_interval %>% int_length(),
         ad_delivery_duration_day = ad_delivery_interval / ddays(x = 1),
         start_date = as_date(StartDate),
         start_date_yrmth = floor_date(StartDate, unit = "month"),
         end_date = as_date(EndDate),
         end_date_yrmth = floor_date(EndDate, unit = "month"),
         impressions_per_day = Impressions / ad_delivery_duration_day,
         impressions_per_day_per_dollar = impressions_per_day / Spend
         )

glimpse(add_features)


View(add_features %>% head(1000))

# View(add_features %>% 
#        select(StartDate,
#               EndDate,
#               ad_delivery_duration_sec,
#               ad_delivery_duration_day,
#               start_date,
#               start_date_yrmth,
#               end_date
#               ) %>%
#        head(100)
#      )


rm(data_20182019_long)

```
  
    
  Inspect individual variables.
```{r}

vars_num_wide <-
  add_features %>% 
  select_if(is.numeric) %>% 
  select(-data_yr,
         -ad_delivery_interval
         )

# glimpse(vars_num_wide)
dim(vars_num_wide)


vars_num_long <-
  vars_num_wide %>% 
  pivot_longer(cols = everything(),
               names_to = "variable",
               values_to = "value"
               ) %>% 
  # group_by(variable) %>% 
  # nest() 
  split(.$variable)

glimpse(vars_num_long$ad_delivery_duration_day)


rm(vars_num_wide)

```


```{r}

# vars_num_hist <-
#   vars_num_long %>% 
#   mutate(hist = map(data,
#                     ~ggplot(data = .x,
#                             aes(x = value)
#                             ) +
#                       geom_histogram() +
#                       theme_minimal() +
#                       NULL
#                     ),
#          freq = map(data,
#                     ~ggplot(data = .x,
#                             aes(x = value)
#                             ) +
#                       geom_freqpoly() +
#                       theme_minimal() +
#                       # labs(title = paste0("Histogram of ",
#                       #                     variable
#                       #                     )
#                       #      ) +
#                       NULL
#                     )
#          )
# 
# glimpse(vars_num_hist)
# vars_num_hist$hist
# vars_num_hist$freq

```



```{r}

vars_num_hist_freq <-
  pmap(.l = list(a = vars_num_long,
                 b = names(vars_num_long)
                 ),
       .f = function(a, b) {
         plot_basic =
           a %>% 
           # ggplot(aes(#x = log1p(value)
           #            x = value
           #            ),
           #        ) +
           ggplot() +
           theme_minimal() +
           # scale_x_continuous(labels = comma,
           #                    trans = scales::log1p_trans()
           #                    ) +
           # labs(x = paste0("Log of ", b)
           #      ) +
           NULL
         
         hist =
           plot_basic +
           geom_histogram(aes(x = value),
                          na.rm = TRUE,
                          bins = 50
                          ) +
           scale_x_continuous(labels = comma,
                              trans = scales::log1p_trans()
                              ) +
           labs(title = paste0("Histogram of ",
                               b
                               ),
                subtitle = "logged values",
                x = b
                )
         
         freq =
           plot_basic +
           geom_freqpoly(aes(x = value),
                         na.rm = TRUE,
                         bins = 50
                         ) +
           scale_x_continuous(labels = comma,
                              trans = scales::log1p_trans()
                              ) +
           labs(title = paste0("Freqpoly of ",
                               b
                               ),
                subtitle = "logged values",
                x = b
                )
         
         box =
           plot_basic +
           geom_boxplot(aes(y = value),
                        na.rm = TRUE,
                        outlier.color = "red"
                        ) +
           scale_y_continuous(labels = comma,
                              trans = scales::log1p_trans()
                              ) +
           labs(title = paste0("Boxplot of ",
                               b
                               ),
                subtitle = "logged values",
                x = b
                )
         
         return(list(hist = hist,
                     freq = freq,
                     box = box
                     )
                )
         }
       )

vars_num_hist_freq


rm(vars_num_hist_freq)

```




```{r}

View(add_features %>% 
  count(interests_long,
        sort = TRUE
        )
  )

View(add_features %>% 
  mutate(interests_long_lump = fct_lump(f = interests_long,
                                        prop = 0.01,
                                        # n = 20,
                                        other_level = "_Other"
                                        )
         ) %>% 
  count(interests_long_lump,
        sort = TRUE
        )
  )

```


```{r}

smry <-
  add_features %>% 
  select_if(is.character) %>% 
  mutate_all(factor) %>% 
  summary()

str(smry)
smry
# View(smry %>% as.data.frame())



chr_cols <-
  add_features %>% 
  select_if(is.character) %>% 
  colnames()

names(chr_cols) <- chr_cols
# str(chr_cols)


cnt_within_chr_cols <-
  pmap(.l = list(a = chr_cols
                 ),
       .f = function(a) { #, b) {
         quo_a = enquo(a)
         
         data_count = add_features %>% 
           count(!!!rlang::parse_exprs(a),
                 sort = TRUE,
                 name = "cnt_n"
                 ) %>% 
           mutate(is_na = if_else(is.na(!!!rlang::parse_exprs(a)
                                        ),
                                  0,
                                  1
                                  )
                  ) %>% 
           arrange(desc(is_na),
                   desc(cnt_n)
                   ) %>% 
           mutate(cnt_n_cumsum = cumsum(cnt_n),
                  cnt_pct = cnt_n / sum(cnt_n),
                  cnt_pct_cumsum = cumsum(cnt_pct),
                  row_num = row_number(),
                  row_num_pct = row_num / max(row_num)
                  )
         
         return(data_count)
         }
       )

cnt_within_chr_cols
# cnt_within_chr_cols$interests_long

```




